### 2018-07-11 FrascatiPlot/Paper/NucleiB2.tex
Updated figures and minor fixes to caption, just because we are precise...

\begin{figure}[htbp]
	\begin{center}
		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the coalescence prediction for two different mappings of the \avdNdeta to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo values in central Pb-Pb collisions.}
		\label{fig:CompareB2B3forDifferentParamWithData}
	\end{center}
\end{figure}

@@

\begin{align}
	{\rm d}R{\rm d}r_{1}{\rm d}r_{2}{\rm d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
		{\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
			{1\over 4} & 0 & 1 & -{1\over 3}  \\
			{1\over 4} & 0 & 0 & 1
			 \end{vmatrix} {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \\
		&= 1 \cdot {\rm d}x_{1}{\rm d}x_{2}{\rm d}x_{3}{\rm d}x_{4} \; .
\end{align}

\noindent From the requirement $\int|\phi|^2{\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:

\begin{align}
	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}
\end{align}

\noindent where the integration in spherical coordinates is performed with ${\rm d}\vec{r}_{1} = 4\pi r_{1}^{2}{\rm d}r_{1},  {\rm d}\vec{r}_{2} = \ldots$ which gives

\begin{align}
	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  {\rm d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  {\rm d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  {\rm d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
\end{align}

@@

\begin{align}
	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 {\rm d}\vec{x}_{1}{\rm d}\vec{x}_{2}{\rm d}\vec{x}_{3}{\rm d}\vec{x}_{4} \\
	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} \\
	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm I} \\
	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm II} \\
	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3}}_{\rm III}
				 \Bigr)
\end{align}

\noindent The first summand I can be calculated with ${\rm d}\vec{r}_{1}{\rm d}\vec{r}_{2}{\rm d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 {\rm d}r_{1}{\rm d}r_{2}{\rm d}r_{3}$ as

\begin{align}
 {\rm I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr){\rm d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) {\rm d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) {\rm d}r_{3} \\
 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
\end{align}

@@

\begin{align}
	\lambda_{4}^{2} &= {C_4^2 \over 4} ({\rm I} + {\rm II} + {\rm III} ) \\
	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
	&= {9 \over 8 \nu_A} \;.
\end{align}

>>>>

\begin{figure}[htbp]
	\begin{center}
		\includegraphics[width=\textwidth]{radiiParamCompareData.png}
		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the coalescence prediction for two different mappings of the \avdNdeta~to the system size $R$: (left panels) the parameterisation fitted to the HBT radii, (right panels) the parameterisation tuned to the \btwo~values in central Pb-Pb collisions.}
		\label{fig:CompareB2B3forDifferentParamWithData}
	\end{center}
\end{figure}

@@

\begin{align}
	\mathrm{d}R\mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3} &= \vert\det {\partial(R,r_{1},r_{2},r_{3}) \over \partial(x_{1},x_{2},x_{3},x_{4})}\vert \; \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
		&= \begin{vmatrix} {\partial R \over \partial x_{1}} & {\partial r_{1} \over \partial x_{1}} & {\partial r_{2} \over \partial x_{1}}& {\partial r_{3} \over \partial x_{1}} \\ 
		{\partial R \over \partial x_{2}} & {\partial r_{1} \over \partial x_{2}} & {\partial r_{2} \over \partial x_{2}}& {\partial r_{3} \over \partial x_{2}} \\ 
		{\partial R \over \partial x_{3}} & {\partial r_{1} \over \partial x_{3}} & {\partial r_{2} \over \partial x_{3}}& {\partial r_{3} \over \partial x_{3}} \\ 
		{\partial R \over \partial x_{4}} & {\partial r_{1} \over \partial x_{4}} & {\partial r_{2} \over \partial x_{4}}& {\partial r_{3} \over \partial x_{4}} \end{vmatrix} 
		\mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
		&=  \begin{vmatrix} {1\over 4} & -1 & -{1\over 2} & -{1\over 3}  \\
			{1\over 4} & 1 & -{1\over 2} & -{1\over 3}  \\
			{1\over 4} & 0 & 1 & -{1\over 3}  \\
			{1\over 4} & 0 & 0 & 1
			 \end{vmatrix} \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \\
		&= 1 \cdot \mathrm{d}x_{1}\mathrm{d}x_{2}\mathrm{d}x_{3}\mathrm{d}x_{4} \; .
\end{align}

\noindent From the requirement $\int|\phi|^2\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = 1$, we thus obtain for the normalisation constant $C_4$:

\begin{align}
	{1\over C_{4}^{2}} &= \int \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}
\end{align}

\noindent where the integration in spherical coordinates is performed with $\mathrm{d}\vec{r}_{1} = 4\pi r_{1}^{2}\mathrm{d}r_{1},  \mathrm{d}\vec{r}_{2} = \ldots$ which gives

\begin{align}
	{1\over C_{4}^{2}} &= (4\pi)^{3} \underbrace{\int_{0}^{\infty} r_{1}^{2}\exp\Bigl(-{1\over 2} \nu_{4}  r_{1}^{2}  \Bigr)  \mathrm{d}r_{1}}_{{\sqrt{\pi} \over 4} {1 \over ({1\over 2} \nu_{4})^{3/2}}  }
							\underbrace{\int_{0}^{\infty} r_{2}^{2}\exp\Bigl(-{2\over 3} \nu_{4}  r_{2}^{2}  \Bigr)  \mathrm{d}r_{2}}_{{\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{4})^{3/2}}  }
							\underbrace{\int_{0}^{\infty} r_{3}^{2}\exp\Bigl(-{3\over 4} \nu_{4}  r_{3}^{2}  \Bigr)  \mathrm{d}r_{3}}_{{\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{4})^{3/2}}  } \\
		&= \bigl({\pi \over \nu_{A}}\bigr)^{9/2} 4^{3/2} \\
	\Rightarrow C_{4} &= \Bigl({\nu_{A}^{3} \over 4 \pi^{3}}\Bigr)^{3/4} \;.
\end{align}

@@

\begin{align}
	\lambda_{4}^{2} &= {1 \over 4} \langle \phi \vert   \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 \vert \phi \rangle \\
	&= \int {1\over 4}  \sum_{i=1}^{4}(\vec{x}_{i} - \vec{X})^2 |\phi|^2 \mathrm{d}\vec{x}_{1}\mathrm{d}\vec{x}_{2}\mathrm{d}\vec{x}_{3}\mathrm{d}\vec{x}_{4} \\
	 &= {C_4^2 \over 4}  \int \bigl({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2} \bigr) \exp^{2}\Bigl(-{1\over 2} \nu_{4} ({1\over 2}r_{1}^{2} + {2\over 3} r_{2}^{2} + {3\over 4}r_{3}^{2}) \Bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} \\
	&= {C_4^2 \over 4} \Bigl(\underbrace{{1\over 2} \int r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{I}} \\
	&\;\;+ \underbrace{{2\over 3} \int r_{2}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{II}} \\
	&\;\;+ \underbrace{{3\over 4} \int r_{3}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr) \exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3}}_{\mathrm{III}}
				 \Bigr)
\end{align}

\noindent The first summand I can be calculated with $\mathrm{d}\vec{r}_{1}\mathrm{d}\vec{r}_{2}\mathrm{d}\vec{r}_{3} = (4\pi)^3 r_1^2 r_2^2 r_3^2 \mathrm{d}r_{1}\mathrm{d}r_{2}\mathrm{d}r_{3}$ as

\begin{align}
 \mathrm{I} &= {1\over 2} (4\pi)^3 \cdot \int_{0}^{\infty} r_{1}^2 \exp\bigl(-{1\over2} \nu_A r_{1}^{2}\bigr)\mathrm{d}r_{1} \cdot \int_{0}^{\infty}\exp\bigl(-{2\over3} \nu_A r_{2}^{2}\bigr) \mathrm{d}r_{2} \cdot \int_{0}^{\infty} \exp\bigl(-{3\over4} \nu_A r_{3}^{2}\bigr) \mathrm{d}r_{3} \\
 	&= {1\over 2} (4\pi)^3 \cdot {3\sqrt{\pi} \over 8} {1 \over ({1\over 2} \nu_{A})^{5/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({2\over 3} \nu_{A})^{3/2}} \cdot {\sqrt{\pi} \over 4} {1 \over ({3\over 4} \nu_{A})^{3/2}} \;.
\end{align}

@@

\begin{align}
	\lambda_{4}^{2} &= {C_4^2 \over 4} (\mathrm{I} + \mathrm{II} + \mathrm{III} ) \\
	&= {C_4^2 \over 4} (4\pi)^3 {3\pi^{3/2} \over 8 \cdot 4^2 \cdot \nu_A^{11/2}} \underbrace{\Bigl({{1\over2} \over ({1\over2})^{5/2}({2\over3})^{3/2}({3\over4})^{3/2} } +
	{{2\over3} \over ({1\over2})^{3/2}({2\over3})^{5/2}({3\over4})^{3/2} } + {{3\over4} \over ({1\over2})^{3/2}({2\over3})^{3/2}({3\over4})^{5/2} } \Bigr)}_{= 24} \\
	&= {9 \over 8 \nu_A} \;.
\end{align}
